\begin{frontmatter}[Dedication]
    \centering
    ``Ohana significa familia, y tu familia nunca te abandona, ni te olvida.''\\
    --- Stitch, Lilo \& Stitch

    \justify
    Malle santa, cuando te hablé desde el trabajo para darte la noticia me dijiste que siempre lo supiste. Recuerdo que lloraste en el teléfono, se te cerró la garganta y a mí también. A diferencia de otras veces, no pudimos platicar mucho porque nos quedamos sin aliento. Así que le hablaste a abuelita Raquel mientras le hablé a papá. Madre, David y yo te debemos tanto que no podemos pagar en mil vidas, pero ten por seguro que eres nuestro ejemplo a seguir. Como nuestra madre chingona y chambeadora, solo hay una y como ella no hay ninguna. Sin ti, el mundo sería un lugar más cruel y pobre, no merece un ángel tan grande y puro como tú.

    Dad, ``Igualito que tu jefe, wey.'' con tu risa característica fue lo primero que dijiste cuando te llamé para darte la noticia ``Sí dad, igualito que mi jefe.'' Entre risa respondí. Como siempre, no platicamos mucho, pero esa vez porque le querías decir a abuelita Teté y a mis tíos, y yo le quería avisar a David. Pensé que seguirías aquí para carcajearte al verme en la túnica ridícula, así como lo hicimos nosotros cuando te vimos en la tuya. Escribo esta dedicatoria antes de acabar porque lo prometido es deuda y esta madre la voy a acabar. No te tendremos para pedirte consejos y contarte de nuestros avances y tropiezos, pero a veces escucho tu voz cuando veo la luna y las estrellas me siguen a donde voy. Te queremos y extrañamos muchísimo. Buenas noches, dad.

    David, ``Te mamaste we.'' Me dijiste cuando me abrazaste al llegar a casa después del trabajo el día que me aceptaron. Me has hecho falta, te extraño mucho. Perdón por no hablar tan seguido, pero me duele colgar. No estoy tan chisqueado como mamá, pero siento feito cuando terminamos de platicar. Me gusta mucho ver tus streams porque me recuerda un poco a sentarme a tu lado para verte jugar, a cuando veíamos a Forsen o TB ``missing legal'', el hype de ver a Mang0 irse off-stage contra HBox, y ver los torneos de CSGO.

    Esto es para mi Ohana por sangre y por elección. Ustedes creyeron en mí cuando yo no lo hacía. Me empujaron a ser mejor. Me extendieron la mano cuando nadie más lo hizo. Me hicieron reír cuando solo sabía llorar. Gracias por hacerme quien soy.
\end{frontmatter}

\begin{frontmatter}[Acknowledgements]

    \begin{justify}
        I did not get here alone. Truly I don't have much idea what I did to deserve the help and encouragement of such an eclectic mix of incredible people. The list is long, but like the proverbial beating of a butterfly's wings, there is no telling where I'd be without the aid and support of these people.

        First and foremost, my supervisors Ed Tarleton and Angus Wilkinson. Thank you for believing in me; thank you for the knowledge and advice; but most of all, thank you for your kindness when my life fell apart.

        Alan Xu and Dhriti Bhattacharyya for so kindly providing ample, high quality experimental data for me to look at and attempt to explain with EasyDD.

        Adrian Taylor, Marion Beckett, Philippa Moss, and Rebecca ``Becs'' Bradford. Thank you for stepping in when my own country turned its back on me. Thank you for all your help, for your kindness and your encouraging words. It means the world to me.

        Kathryn Harvey, Kate Lancaster, Roddy Vann, Howard Wilson, Ruth Lowman, Donna Cook and the rest of the Fusion CDT, thank you for such an incredible experience. I had so much fun, made a ridiculous amount of life-long friends, and carry with me so many awesome memories. We have you to thank for bringing an eclectic, yet oddly harmonious group of people that I now consider some of my closest friends. The holidays together, gaming nights, Christmas Carnages, overcrowded hot tubs, weddings and other miscelaneous excuses we have made to get together have always been thoroughly enjoyable.

        ``It's later than you think\ldots{} But it's never too late'' I never thought the unofficial Harris-Manchester motto would apply to my DPhil, yet here we are. Vicky Lill, Annette Duffel, Sue Killoran and Ralph Waller, thank you for everything. And very special thank you to the man, the legend, the gamer, and college MVP, John Carter---I cannot think of anyone who embodies the spirit of HMC more than you do, mate.

        My friends and colleagues in the Tarleton Research Group, Haiyang Yu, Fenxian Liu and Daniel Hortelano-Roig for all the fruitful discussions, ideas, advice and help along the way. A special thank you to Bruce Bromage---also of the Tarleton Research Group---whose DPhil ran parallel to mine; your penchant for incessantly antagonising my less-than-great ideas, as well as for code archaeology, and the mammoth lengths you went to, led to a much improved EasyDD.

        Damian Rouson of Sourcery Institute fame. I could not have chosen a better collaboratory. Thank you for the hospitality, the sights, and the experiences. The Sourcery Institute wizard hat is the most valuable possesion I gained during my DPhil, I wear it sometimes when I'm stuck on something and need cosmic insight.

        My former supervisors and mentors, Marcelo F. Videa, Anatoly B. Kolomeisky and John F. Stanton, thank you for giving me a chance when I was green and unproven. I hope to have made you proud.

        ``OUPLC'' thank you for the memes, the hype, the gains, the friendships, and most of all, for showing me that perhaps the heaviest things that we lift are not our weights, but our feels.

        ``Kopse Lane Krump v1.0 \& v2.0'' thank you for being such great friends and housemates. Thank you for having me over for Christmas so I wouldn't be alone, it meant the world to me. But most of all, thank you for being there when my life turned to dust.

        ``Goosehood'', si algo bueno salió del fever dream que compartimos, es nuestra amistad. Hicieron que aquellos días fueran tolerables. Gracias amigoes.

        ``Clan del Rano Sentado'', no podría haber elegido mejores compañeros para este viaje místico repleto de manómetros rotos, desacoplados, y conectados al morado cósmico.

        ``La Isla'', \sout{mis amigos} mi Ohana elegida desde mi retorno a México en el 2008. Para bien o para mal, hemos compartido una buena parte del espectro de experiencias y emociones que ofrece la vida\ldots{} Witness me!
    \end{justify}

\end{frontmatter}
