\addtocounter{chapter}{-1}
\chapter{Preface}
\label{c:pre}

\section{Notation and abbreviation}
\label{s:nota}

For the sake of clarity the following notation and abbreviation conventions have been used:
\begin{itemize}
	\item GPU: Graphics Processing Unit.
	\item CPU: Central Processing Unit.
	\item Tensors are denoted by sans serif bold italics, $ \tns{T} $.
	\item Matrices are denoted by serif bold Roman, $ \mtx{M} $.
	\item Vectors are denoted by serif bold italics, $ \vec{V} $.
	\item Scalars are denoted by serif italics, $ S $.
	\item Operators and special functions are Roman, $\exp(x)$, $\det{\left(\mtx{J}\right)}$.
	\item 2-norms are denoted by double vertical pipes $\lVert \vec{a} \rVert$.
	\item Absolute values are denoted by single vertical $\lvert a \rvert$.
	\item Angles are in radians unless otherwise stated.
	\item Einstein notation for tensor components is used unless otherwise stated.
	\item Individual items, be they nodes, surface elements, dislocation segments or indices are denoted by a lower-case subscript to the right, $a_n$.
	\item Ensembles are denoted by an upper-case subscript to the right, $a_N \coloneqq \sum a_n$.
	\item Host variables (CPU variables in parallelisation) are denoted by a Roman h-superscript on the left, $\hvar{a}$.
	\item Global device variables (global variables visible only to the GPU) are denoted by a Roman d-superscript on the left, $\dvar{a}$.
	\item Thread variables (variables visible only to a GPU thread) are denoted by a Roman t-superscript on the left, $\tvar{a}$.
	\item Serial indices/counters are the traditional $i$, $j$, $k$, etc.
	\item Parallel indices are denoted as Roman variables, $\rvar{a}$.
	\item Pseudo-code is C-style---row-major order, 0-based indexing---because it provides a more direct translation of the C-code.
	\item Big-O, $\mathcal{O}$, Big-Theta, $\Theta$, and Big-Omega, $\Omega$, notation are used to respectively denote upper, mean and lower asymptotic bounds.
\end{itemize}

\section{Typesetting}
\label{s:typeset}

In the digital version of this document, \href{https://www.youtube.com/watch?v=eh7lp9umG2I}{URLs}, commits, and filenames are hyperlinks to the relevant websites.

The repository \href{https://github.com/dcelisgarza/latex_templates}{https://github.com/dcelisgarza/latex\_templates} contains the custom document class used to typeset this document. It was compiled with \hologo{XeLaTeX} and \hologo{BibTeX}. We recommend compiling the source with \hologo{XeLaTeX} or \hologo{LuaLaTeX}. Requires \texttt{minted}, \href{https://ctan.org/pkg/minted?lang=en}{\texttt{https://ctan.org/pkg/minted?lang=en}} and its dependencies to compile.
\section{Diagrams}
\label{s:diag}

All diagrams were drawn with Inkscape: Open Source Scalable Vector Graphics Editor, \href{https://inkscape.org/}{\texttt{https://inkscape.org/}}, ``Draw Freely.''

\section{COVID-19 Impact Statement}

I didn't want to write this, I was suggested to include it. I have a hard time admitting defeat, I refuse. But to say my life, work, and outlook have not been impacted would be a lie.

2019 was a horrible year for me personally. It began with me injuring both wrists. The right, my dominant side, was very seriously injured.

On the day between the first and second surgeries, I was told I would lose 25\% of the use of my dominant hand. As an avid powerlifter, calisthenics practitioner, and gaming fanatic, I was devastated. I promised the surgeon I would prove him wrong. A few hours later, as I planned my glorious comeback, I received a call from home. There was something seriously wrong with my dad's health.

I went back to the office three days after the second surgery, still wearing the surgical cast. I tried working, but the fracture on my left wrist was extremely bothersome and quite painful. It took two more tries for me to accept that I was going to need some time off.

After almost eight weeks, I had the final cast taken off, as well as the third and last surgery. I was given a strict rehabilitation protocol; as many sessions as I could tolerate, every day, for six months. Every session was gruelling, painful, and long. But I didn't want 75\%, I wanted my hand back. I had a goal.

Sadly, my dad was taken to hospital a week later. He was gone in less than three days. Died the morning of the day I was flying home. His last conversation was with me, through my brother's phone, a few hours before dying. I am as far from religious as can be, but sometimes I get jealous of those who are.

I spent two weeks home, obsessively sticking to my rehab, putting on a smiling, determined face. As I sat on the Heathrow-Oxford coach, I logged into my institutional email. I wanted to get back to work, I promised I would. But the first email I read had the ominous subject, ``About the incident in college last night''. A friend had committed suicide in their room.

I broke.

Walking back home from the bus stop, I caught sight of the clouds. They shimmered and sparkled prettily. It took some time for me to realise that I was looking at them through tears. I got home and did my rehab.

I met with Ed and Angus a few days later, but I could barely speak for all my crying. Angus got me some psychological help, but it took me a week to fill out the form. I suspended my status, and slowly, I healed.

I was allowed to cycle in July, five months after the second surgery. A month later, I was allowed to go back to training. I officially restarted my status in October, but if I'm being honest, I didn't begin to feel remotely close to myself until January 2020.

As I caught my stride, the pandemic began. Both my housemates left a few days before the first lockdown. They never came back. What little progress I had made, broke down after four weeks of lockdown. On the first anniversary of my dad going to hospital to die. I was back in the nightmare, but this time I was alone.

My funders---who had been \emph{extremely} troublesome in the past, and still owe me a not insignificant sum of money---have proven to be unresponsive, incompetent, and uncaring. They even blamed me for their inability to update their own database. As such, I want it to be known that this is the only mention they get, I have gone back and removed their name and logo from all my previous works. I will \emph{never} work with them again. I must extend my unbridled gratitude to the Fusion CDT and the Department of Materials who have, in no small terms, stepped in to save the day. It is a sad state of affairs when one's country has no vested interest in the people who represent them internationally. Their loss.

All this turmoil has affected my life, my work, and my outlook. I hate to admit it, but it's true. I expected a lot more of myself. I don't want clemency or leniancy, I want to be judged by what is on these pages, not by what could have been or what I've been through. This section was a late addition to the thesis, and I hate it.

As a final note, I'm happy to report that my hand has pretty much fully recovered. I have about 95\% of the range of motion back, and all kinds of grip strength have recovered and exceeded what they once were. I don't \emph{need} wrist wraps any more and can once again do handstands, some day I'll do a planche too. The hard rehab paid off.
\savearabiccounter
% 283 words
